Imperative Programming with Variational Effects

### 2018-07-12 paper/paper.tex
more inference rules

@@

>>>>

\def \nothing {\bullet}
\def \BigErr {\infer [S-Err] { } {(\mathit{err}\ n,S,s) \Downarrow_S (\mathit{err}\ n,S)}}
\def \BigSkip {\infer [S-Skip] { } {(E,S,\text{skip}) \Downarrow_S (E,S)}}
\def \BigAssn {\infer [S-Assn] {(S,e) \Downarrow_A n} {(\nothing,S,x \coloneqq e) \Downarrow_S (\nothing,S[x \rightarrow n])}}
\def \BigSeq {\infer [S-Seq] {(E,S,s) \Downarrow_S (E',S') \\ (E',S',s') \Downarrow_S (E'',S'')} {(E,S,s\ \text{seq}\ s') \Downarrow_S (E'',S'')}}
\def \BigIfT {\infer [S-IfT] {(S,e) \Downarrow_B \mathit{true} \\ (\nothing,S,s) \Downarrow_S (E,S')} {(\nothing,S,\text{if}\ e\ \text{then}\ s\ \text{else}\ s') \Downarrow_S (E,S')}}
\def \BigIfF {\infer [S-IfF] {(S,e) \Downarrow_B \mathit{false} \\ (\nothing,S,s') \Downarrow_S (E,S')} {(\nothing,S,\text{if}\ e\ \text{then}\ s\ \text{else}\ s') \Downarrow_S (E,S')}}
\def \BigWhileT {\infer [S-WhileT] {(S,e) \Downarrow_B \mathit{true} \\ (\nothing,S,s) \Downarrow_S (E,S') \\ (E,S',\text{while}\ e\ \text{do}\ s) \Downarrow_S (E',S'')} {(\nothing,S,\text{while}\ e\ \text{do}\ s) \Downarrow_S (E',S'')}}
\def \BigWhileF {\infer [S-WhileF] {(S,e) \Downarrow_B \mathit{false}} {(E,S,\text{while}\ e\ \text{do}\ s) \Downarrow_S (E,S)}}
\def \BigThrow {\infer [S-Throw] {(S,e) \Downarrow_A n} {(\nothing,S,\text{throw}\ e) \Downarrow_S (\mathit{err}\ n,S)}}
\def \BigTry {\infer [S-Try] {(\nothing,S,s) \Downarrow_S (\nothing,S')} {(\nothing,S,\text{try}\ s\ \text{catch}\ x\ \text{in}\ s') \Downarrow_S (\nothing,S')}}
\def \BigCatch {\infer [S-Catch] {(\nothing,S,s) \Downarrow_S (\mathit{err}\ n,S') \\ (\nothing,S'[x \rightarrow n],s') \Downarrow_S (E,S'')} {(\nothing,S,\text{try}\ s\ \text{catch}\ x\ \text{in}\ s') \Downarrow_S (E,S''[x \rightarrow S'(x)])}}

\begin{mathpar}
\BigErr \and
\BigSkip \and
\BigAssn \and
\BigSeq \and
\BigIfT \and
\BigIfF \and
\BigWhileT \and
\BigWhileF \and
\BigThrow \and
\BigTry \and
\BigCatch
\end{mathpar}

@@

\def \BigVNum {\infer [VA-Num] { } {(C,S,n) \Downarrow_{VA} n}}
\def \BigVRef {\infer [VA-Ref] { } {(C,S,x) \Downarrow_{VA} S(C,x)}}
\def \BigVAdd {\infer [VA-Add] {(C,S,e) \Downarrow_{VA} v \\ (C,S,e') \Downarrow_{VA} v'} {(C,S,e+e') \Downarrow_{VA} \mathit{liftV2}(+,v,v')}}
\def \BigVAChcOne {\infer [VA-Chc1] {\mathit{sat}(C \wedge A) \\ \mathit{sat}(C \wedge \neg A) \\ (C \wedge A,S,e) \Downarrow_{VA} v \\ (C \wedge \neg A,S,e') \Downarrow_{VA} v'} {(C,S,\tagtree{A}{e}{e'}) \Downarrow_{VA} \tagtree{A}{v}{v'}}}
\def \BigVAChcTwo {\infer [VA-Chc2] {\mathit{unsat}(C \wedge A) \\ \mathit{sat}(C \wedge \neg A) \\ (C \wedge \neg A,S,e') \Downarrow_{VA} v'} {(C,S,\tagtree{A}{e}{e'}) \Downarrow_{VA} \tagtree{A}{\nothing}{v'}}}
\def \BigVAChcThree {\infer [VA-Chc3] {\mathit{sat}(C \wedge A) \\ \mathit{unsat}(C \wedge \neg A) \\ (C \wedge A,S,e) \Downarrow_{VA} v} {(C,S,\tagtree{A}{e}{e'}) \Downarrow_{VA} \tagtree{A}{v}{\nothing}}}
\def \BigVAChcFour {\infer [VA-Chc4] {\mathit{unsat}(C \wedge A) \\ \mathit{unsat}(C \wedge \neg A)} {(C,S,\tagtree{A}{e}{e'}) \Downarrow_{VA} \nothing}}

\def \BigVB {\infer [VB-Bool] { } {(C,S,b) \Downarrow_{VB} b}}
\def \BigVNot {\infer [VB-Not] {(C,S,e) \Downarrow_{VB} v} {(C,S,\text{not}\ e) \Downarrow_{VB} \mathit{liftV}(\neg,v)}}
\def \BigVAnd {\infer [VB-And] {(C,S,e) \Downarrow_{VB} v \\ (C,S,e') \Downarrow_{VB} v'} {(C,S,e\ \text{and}\ e') \Downarrow_{VB} \mathit{liftV2}(\wedge,v,v')}}
\def \BigVLess {\infer [VB-Less] {(C,S,e) \Downarrow_{VA} v \\ (C,S,e') \Downarrow_{VA} v'} {(C,S,e<e') \Downarrow_{VB} \mathit{liftV2}(<,v,v')}}
\def \BigVBChcOne {\infer [VB-Chc1] {\mathit{sat}(C \wedge A) \\ \mathit{sat}(C \wedge \neg A) \\ (C \wedge A,S,e) \Downarrow_{VB} v \\ (C \wedge \neg A,S,e') \Downarrow_{VB} v'} {(C,S,\tagtree{A}{e}{e'}) \Downarrow_{VB} \tagtree{A}{v}{v'}}}
\def \BigVBChcTwo {\infer [VB-Chc2] {\mathit{unsat}(C \wedge A) \\ \mathit{sat}(C \wedge \neg A) \\ (C \wedge \neg A,S,e') \Downarrow_{VB} v'} {(C,S,\tagtree{A}{e}{e'}) \Downarrow_{VB} \tagtree{A}{\nothing}{v'}}}
\def \BigVBChcThree {\infer [VB-Chc3] {\mathit{sat}(C \wedge A) \\ \mathit{unsat}(C \wedge \neg A) \\ (C \wedge A,S,e) \Downarrow_{VB} v} {(C,S,\tagtree{A}{e}{e'}) \Downarrow_{VB} \tagtree{A}{v}{\nothing}}}
\def \BigVBChcFour {\infer [VB-Chc4] {\mathit{unsat}(C \wedge A) \\ \mathit{unsat}(C \wedge \neg A)} {(C,S,\tagtree{A}{e}{e'}) \Downarrow_{VB} \nothing}}

\begin{mathpar}
\BigVNum \and
\BigVRef \and
\BigVAdd \and
\BigVAChcOne \and
\BigVAChcTwo \and
\BigVAChcThree \and
\BigVAChcFour \and
\BigVB \and
\BigVNot \and
\BigVAnd \and
\BigVLess \and
\BigVBChcOne \and
\BigVBChcTwo \and
\BigVBChcThree \and
\BigVBChcFour
\end{mathpar}
